Titeln på avhandlingens språk

### 2022-11-05 background.tex
add James comments as todonotes

@@

@@

\subsection{The effects of changes in responsiveness on human behavior}\label{ssec:plos}

>>>>

\todo[inline]{%
Talk about sampling, but don’t introduce greedy right away. First explain the sampling process generally (why is sampling necessary?) and then mention that different sampling strategies exist, for instance greedy ….
}

@@

\todo[inline]{%
Again, turn it around. The uniform distribution is less relevant than the terms execution time, wait time and last sample etc. Introduce the distribution at the end of the paragraph.
}

@@

\subsection{The effects of changes in responsiveness on human behavior}\label{ssec:plos}
\todo[inline]{Shorten}

### 2022-11-05 intro.tex
working
add James comments as todonotes

We name the new model presented in this paper \emph{EdgeDroid \num{2.0}}; a direct, more realistic evolution of our initial EdgeDroid approach.
\todo[inline]{What is our goal with this?}

@@

>>>>

We name the new model presented in this paper \emph{\edgedroid}; a direct, more realistic evolution of our initial EdgeDroid approach.
\todo[inline]{What is our goal with this?}

@@

\todo[inline]{%
Nice intro. Perhaps too long, and a concise presentation - preferably as bullet list - of the contributions is missing. Try to shorten in particular for the first three paragraphs. Another question would be if there is no other related work. For instance, Zorzi recently published a model for AR and VR - trace-based - that would be a good reference to have. 
}
